\documentclass[11pt]{article}

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{enumerate,comment}
\usepackage{url}
\usepackage{color}
\usepackage[margin=1.2in]{geometry}
\usepackage{fancyhdr}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{cleveref}
\usepackage{mdframed}

\pagestyle{fancy}
\setlength{\headheight}{20pt}
\setlength{\headsep}{20pt}
\fancyhead[L]{\small{CS 276, Fall 2024}}
\fancyhead[R]{\small{Prof. Sanjam Garg}}

\newcommand\custombox[2]{%%
    \fbox{\rule{#1}{0pt}\rule[-0.5ex]{0pt}{#2}}}

\newcommand\answerbox{%%
    \fbox{\rule{1in}{0pt}\rule[-0.5ex]{0pt}{4ex}}}

\newtheorem{theorem}{Theorem}[section]
\newtheorem{definition}[theorem]{Definition}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{claim}[theorem]{Claim}
\newtheorem{fact}[theorem]{Fact}
\newtheorem{conjecture}[theorem]{Conjecture}
\newtheorem{remark}[theorem]{Remark}
\newenvironment{assumption}{\noindent{\bf Assumption}\hspace*{1em}\begin{em}}{\end{em}\medskip}
\newenvironment{solution}{\color{blue}\noindent{\bf Solution}\hspace*{1em}}{\qed\medskip}

\numberwithin{equation}{section}

% Crypto terms
\newcommand{\Gen}{\mathsf{Gen}}
\newcommand{\Enc}{\mathsf{Enc}}
\newcommand{\Dec}{\mathsf{Dec}}
\newcommand{\gen}{\mathsf{Gen}}
\newcommand{\enc}{\mathsf{Enc}}
\newcommand{\dec}{\mathsf{Dec}}
\newcommand{\Sign}{\mathsf{Sign}}
\newcommand{\sign}{\mathsf{Sign}}
\newcommand{\Verify}{\mathsf{Verify}}
\newcommand{\verify}{\mathsf{Verify}}
\newcommand{\MAC}{\mathsf{MAC}}
\newcommand{\mac}{\mathsf{Mac}}
\newcommand{\pk}{\mathsf{pk}}
\newcommand{\sk}{\mathsf{sk}}

% mathbb
\newcommand{\bbE}{\mathbb{E}}
\newcommand{\bbF}{\mathbb{F}}
\newcommand{\bbG}{\mathbb{G}}
\newcommand{\bbZ}{\mathbb{Z}}

% mathcal
\newcommand{\cA}{\mathcal{A}}
\newcommand{\cB}{\mathcal{B}}
\newcommand{\cC}{\mathcal{C}}
\newcommand{\cD}{\mathcal{D}}
\newcommand{\cF}{\mathcal{F}}
\newcommand{\cG}{\mathcal{G}}
\newcommand{\cH}{\mathcal{H}}
\newcommand{\cK}{\mathcal{K}}
\newcommand{\cM}{\mathcal{M}}

% Words
\newcommand{\Rank}{\mathsf{Rank}}
\newcommand{\GF}{\mathsf{GF}}
\newcommand{\msg}{\mathsf{msg}}
\newcommand{\negl}{\mathsf{negl}}
\newcommand{\nonnegl}{\mathsf{nonnegl}}
\newcommand{\st}{\mathsf{st}}
\newcommand{\adv}{\cA}
\newcommand{\hyb}{\mathsf{Hyb}}

% Math Notation
\newcommand{\getsr}{\stackrel{\$}{\gets}}
\newcommand{\bin}{\{0,1\}}
\newcommand{\bit}{\bin}
\newcommand{\qed}{\hspace*{\fill}\rule{7pt}{7pt}}

\newcommand{\duedate}{Sept. 13th, 2024 at 8:59pm via Gradescope}

\newif\ifsol
\soltrue

\begin{document}
\section*{CS 276: Homework 2\\ {\small Due Date: \duedate} }

\section{One-Way Functions}
The security of a PRF is only guaranteed if the key is kept secret. However, GGM86's PRF construction still retains some form of security (namely weak one-wayness) even if the key is leaked.

\begin{definition}[GGM86 Function Ensemble]\label{def:GGM-PRF}
    Let $G:\bit^n \to \bit^{2n}$ be a PRG, where $G_0(s)$ outputs the first $n$ bits of $G(s)$ and $G_1(s)$ outputs the last $n$ bits of $G(s)$.
    
    For any seed $s \in \bit^n$, and any input $x = (x_1, \dots, x_n) \in \bit^n$, let the function $f^G_s: \bit^n \to \bit^n$ be defined as follows:
    \[f^G_s(x_1, \dots, x_n) = G_{x_n}\Big(\dots G_{x_2}\big(G_{x_1}(s)\big) \dots \Big)\]
    We sometimes write $f_s^G$ as $f_s$.
    
    Finally let us define the function ensemble $\cF_G = \{f_s^G\}_{s \in \bit^n}$.
\end{definition}

\begin{definition}[One-Way Function Ensemble]
    Let $\cF = \{f_s\}_{s \in \bit^n}$ be a function ensemble where for every $s \in \bit^n$, $f_s$ maps $\bit^n \to \bit^n$ and is efficiently computable. 
    
    $\cF$ is \textbf{one-way} if for any efficient adversary $\cA$,
    \[\Pr_{\stackrel{s \getsr \bit^n}{x \getsr \bit^n}}\left[\cA(s, f_s(x)) \in f_s^{-1}(f_s(x))\right] \leq \negl(n)\]
\end{definition}

\noindent\textbf{Question:} Prove that $\cF_G$ is one-way, assuming conjecture \ref{conj} below.
\begin{conjecture}\label{conj}
    \[\bbE_{s \getsr \bit^n}\left[\frac{|\mathsf{Img}\left(f_s\right)|}{2^n}\right] \geq 1 - \negl(n)\]
\end{conjecture}

Note: We do not know if this conjecture is true, but it is still possible to prove that $\cF_G$ is \textit{weakly} one-way without the conjecture.

If you're unsure how to get started, try assuming that $f_s$ is one-to-one. This is a useful setting in which to build intuition.

\ifsol
$ $

\begin{solution}
TBD
\end{solution}
\fi

\bibliography{cryptobib/abbrev0,cryptobib/crypto,smoser}
\bibliographystyle{alpha}
\end{document}